\documentclass[a4paper]{article}

% ---------- Margins ----------
\usepackage[left=0.7in, right=0.7in, top=0.5in, bottom=0.5in]{geometry}

% ---------- Links ----------
\usepackage[hidelinks]{hyperref}

% ---------- Lists / Titles ----------

% ---------- Global tight spacing ----------
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\renewcommand{\baselinestretch}{0.84}
\footnotesize

% Compact section spacing
\titlespacing*{\section}{0pt}{0.3ex}{0.5ex}
\titleformat{\section}{\normalsize\bfseries}{}{}{}[]

% Compact bullets (global)
\setlist[itemize]{leftmargin=*, label=\textbullet, nosep, topsep=0.2ex, itemsep=0.2ex, parsep=0pt, partopsep=0pt}

% Thin separator line used under section titles
\newcommand{\sectionline}{%
  \par\vspace{0.2ex}%
  \noindent\rule{\linewidth}{0.25pt}%
  \par\vspace{0.2ex}%
}

% Small vertical spacer between entries
\newcommand{\entryspace}{\vspace{0.35em}}

\begin{document}

\begin{center}
    \textbf{\Large Rohit Sudhakar}\\[-0.25ex]
    (608)-707-2365 \quad|\quad rsudhakar2@wisc.edu \quad|\quad
    \href{https://www.linkedin.com/in/rohit-sudhakar-ce/}{linkedin.com/in/rohit-sudhakar-ce} \quad|\quad Madison, WI
\end{center}

\section*{Education}
\sectionline
University of Wisconsin – Madison \hfill Expected May 2026\\
Bachelor of Science in Computer Engineering: Machine Learning and Data Science track\\
GPA: 3.7/4.00 \hfill Dean’s Honor List\\
Relevant Coursework: Digital System Fundamentals; Signals, Information, and Computation; Discrete Mathematics; Object-Oriented Programming; Python for Data Science and Machine Learning; Electronic Circuits; Machine Organization and Programming.

\section*{Work Experience}
\sectionline

\textbf{Ardent Capital Private Limited — AI Intern \textbar\ India} \hfill May 2025 – Present
\begin{itemize}
    \item Developed an AI-based Banking Transaction Categorization Model processing 1.4M+ transactions; integrated fuzzy matching for rare/unseen categories.
    \item Built a React front-end that allows internal users to upload bank statements, view categorized transactions, analyze summaries, and trigger retraining of the AI model from the website.
    \item Automated internal workflows using Python, enhancing efficiency and accuracy across multiple tasks.
    \item Collaborated with cross-functional teams to integrate AI outputs into dashboards and reporting tools.
\end{itemize}
\entryspace

\textbf{Jubilant Capital — Software Engineering Intern \textbar\ Coimbatore, India} \hfill May 2024 – Aug 2024
\begin{itemize}
    \item Led full-stack development of a client management system (React/Tailwind front-end, Flask/SQL backend), improving efficiency by 20\%.
    \item Strengthened data security via role-based access control and encryption protocols.
    \item Optimized backend APIs and queries for 1,000+ client records, improving performance and reliability.
\end{itemize}
\entryspace

\textbf{Connected \& Autonomous Transportation Systems Lab} \hfill Mar 2024 – May 2024\\
\textbf{Undergraduate Researcher | Madison, WI}
\begin{itemize}
    \item Conducted research on connected and autonomous vehicles; analyzed real-time sensor data using C and MATLAB.
    \item Contributed to improvements in vehicle-to-vehicle communication and safety, achieving a 15\% efficiency gain.
\end{itemize}
\entryspace

\textbf{Infinity Credit Solutions — Software Engineering Intern \textbar\ Coimbatore, India} \hfill May 2023 – Sept 2023
\begin{itemize}
    \item Optimized internal workflows and automated processes using Python and API integrations, increasing productivity by 25\%.
    \item Enhanced Zoho CRM features to meet company needs, improving efficiency and reporting.
\end{itemize}

\section*{Projects}
\sectionline

\textbf{Blackjack Game with FreeRTOS FSM (C \textbar\ FreeRTOS \textbar\ Embedded Systems \textbar\ LCD \textbar\ EEPROM \textbar\ TRNG)} \hfill Mar 2025 – May 2025
\begin{itemize}
    \item Built a state-driven Blackjack game on a microcontroller using FreeRTOS with tasks for each game phase; implemented LCD UI, joystick/button input, EEPROM high-score storage, and TRNG-based shuffling.
    \item Managed inter-task communication with semaphores, queues, and event groups for real-time gameplay synchronization.
    \item Enabled persistent scoring and reliable game state management for repeated plays.
\end{itemize}
\entryspace

\textbf{Client Database Management System (React \textbar\ Tailwind \textbar\ Flask \textbar\ SQL \textbar\ PyMongo)} \hfill Aug 2024
\begin{itemize}
    \item Developed a scalable client database system for 500+ clients with secure backend APIs and optimized SQL queries for 1,000+ records.
    \item Implemented role-based access control and bulk upload, reducing manual data entry by 60\%.
    \item Designed an intuitive React/Tailwind front-end for internal teams, improving usability and navigation efficiency.
\end{itemize}
\entryspace

\textbf{Document Automation Tool (Python \textbar\ Tkinter \textbar\ Docx)} \hfill Jul 2023
\begin{itemize}
    \item Automated generation of over 20 daily documents for banks/NBFCs, cutting processing time by 50\%.
    \item Designed dynamic input templates and automated placeholder replacement in Word documents, reducing errors.
\end{itemize}
\entryspace

\textbf{Graphical Earthquake Monitor and Pathfinder (Java \textbar\ JavaFX \textbar\ Dijkstra’s Algorithm)} \hfill Apr 2024
\begin{itemize}
    \item Developed a real-time map application using JavaFX; empowered by Dijkstra's algorithm for efficient pathfinding, reducing route calculation time by 50\%.
    \item Built an interactive interface that allows users to explore multiple earthquake scenarios and optimized routes for relief planning.
\end{itemize}

\section*{Technical Skills}
\sectionline
Programming: Java, Python, Arduino-based C++,\\
MATLAB, JavaScript, Assembly\\
Frameworks/Libraries: JavaFX, Flask, React, Tailwind CSS, TensorFlow, Keras\\
Databases: MySQL, SQL, MongoDB, Firebase\\
Tools: Git, Docker, Kubernetes, Jupyter, VS Code, PyCharm\\
Dev/Scripting: Bash/Command Line, Object-Oriented Programming, API Development

\end{document}
